Late Pleistocene stone artefact technology at Mau A, Yen Bai, Norther Vietnam

### 2022-02-18 analysis/paper/paper.Rmd
Added extra source for GPA in methods section, edit to methods section.

The outlines formed by the shape landmarks were then normalized for size, orientation, and rotation. We used Generalized Procrustes analysis to strip the flakes in the sample dataset of size, orientation, and rotation, leaving only shape data.  Our methodology for carrying out the PCA on the shape landmarks was inspired by Theska et al. (2020), which also performed 2D landmark data analysis using PCA. Finally, the shape landmark values were analysed by Principal Components Analysis. PCA biplots were created to visualize differences based upon secondary categorical variables, namely flake reduction categories, excavation unit, and mass cluster. The first two primary components were then used to create biplots comparing the shape data to the flake reduction categories, excavation unit, and mass clusters, with the secondary variables being represented by colored outlines on the biplots.

@@

>>>>

The outlines formed by the shape landmarks were then normalized for size, orientation, and rotation. We used Generalized Procrustes Analysis to strip the flakes in the sample dataset of size, orientation, and rotation, leaving only shape data. Generalized Procrustes Analysis (or GPA) is a

Jung & Woo (2019)

Our methodology for carrying out the PCA on the shape landmarks was inspired by Theska et al. (2020), which also performed 2D landmark data analysis using PCA. Finally, the shape landmark values were analysed by Principal Components Analysis. PCA biplots were created to visualize differences based upon secondary categorical variables, namely flake reduction categories, excavation unit, and mass cluster. The first two primary components were then used to create biplots comparing the shape data to the flake reduction categories, excavation unit, and mass clusters, with the secondary variables being represented by colored outlines on the biplots.

@@

Jung, H., & Woo, E. J. (2019). Changes in mandibular ramus shape from the Neolithic to modern periods in Korea. International Journal of Osteoarchaeology, 29(4), 634–643. https://doi.org/10.1002/oa.2759
